% LaTeX resume using res.cls
\documentclass[line,margin]{res}

\usepackage{calc}
\usepackage{enumitem}
\usepackage{amssymb}
\usepackage{url}

\begin{document}

\section{Robert Mitchell}
\hfill github.com/Ahlkanvorez -- robertm.io
\address{robert.mitchell36@gmail.com}

\begin{resume}

\section{EXPERIENCE}
    \textbf{Composer} \\
    \textit{Lead Backend Engineer}
    \hfill February 2021 - Present

    I use Clojure to build the backend of a next-gen automated investing
    tool that backtests, benchmarks, and executes strategies. I also strive to
    put the best of Agile \& DevOps principles into practice to see my team succeed.

    \textbf{ION Geophysical} \\
    \textit{Senior Software Engineer}
    \hfill June 2020 - February 2021 \\
    \textit{Software Engineer}
    \hfill August 2017 - June 2020

    \textbf{DevOps \& Cloud} \\
    I used Ansible, Docker, and Python to automate repeatable test environments
    on-premises and in public clouds such as AWS.

    \textbf{Functional Programming \& Graphs} \\
    I designed an Erlang service to gather geophysical processing history from
    RabbitMQ \& CouchDB in real time, and store it in a Neo4j graph database.

    I created a ReactJS front-end to visualize and traverse those history graphs,
    revealing valuable cost-saving insights about wasteful processing patterns.

    I spent a few weeks teaching another team of developers Erlang, and performed
    code reviews on their contributions. \\

    
\section{EDUCATION}
    \textbf{The University of Texas at Austin} 	\hfill August 2014 - May 2017 \\
    \textit{Bachelor of Science \& Arts,} Mathematics \hfill GPA: 3.7 \\
    \textit{Minor,} Chinese Language \hfill GPA:    4.0
    \begin{description}
        \item \textbf{University Honors} \hfill \\
            Spring 2015, 2016, 2017, Fall 2015, 2016 \\
    \end{description}


\section{SIDE PROJECTS}
    \begin{description}
        \item \textbf{Showcase} \hfill \textbf{robertm.io} \\
          A showcase of some of my side projects, and my personal blog. \\
          Written in Clojure with Ring \& Compojure, deployed on Heroku.

        \item \textbf{7GUIs -- Spreadsheet WebApp} \hfill \textbf{robertm.io/blog/seven-guis} \\
          Seven example GUIs including a functional spreadsheet webapp. \\
          Written in ClojureScript \& Reagent. Live demos are hosted
          on AWS S3 \& CloudFront. Each GitHub repo links to its demo.

        \item \textbf{Roam Parser} \hfill \textbf{robertm.io/blog/parsing-roam} \\
          A ClojureScript library for parsing \& manipulating markup inspired \\
          by Roam research, with a webapp demo hosted on AWS S3 \& CloudFront.
    \end{description}


\section{TECHNICAL SKILLS}
    \begin{description}
        \item \textbf{Languages} \hfill \\
          Fluent: Clojure \& ClojureScript, JavaScript, Erlang \\
          Proficient: Python, Java
        \item \textbf{Web Frameworks} \hfill \\
          Fluent: Reagent, React \\
          Proficient: Re-Frame, Express, Node
    \end{description}

\end{resume}
\end{document}
